Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-02-12 latex/comp_or.tex
Reviewing the mathematical formulation

Given the assumptions, scenarios and parameters described in the previous section, we are ready to present the mathematical modelling of ACLP+RPDP, which is one of the contributions of our work.

@@

Let $S_K = \{s: \{1, \dots, K\} \rightarrow \{1, \dots, K\} \}$ be the set of $K!$ permutations, which correspond to all possible tours (or itineraries) that have $l_0$ as origin and end, passing through the others $K$ nodes.

@@

		{\it Stopping criterion:} & All methods have the same time limit of $0.7$ seconds per node.\\

@@

We use four types of random selections:
\begin{itemize}
	\item $RandomReal(r_1,r_2)$: randomly selects a real number in $[r_1,r_2]$;
	\item $RandomInt(i_1,i_2)$: randomly selects a integer number in $[i_1,i_2]$;
	\item $Roulette(set)$ biased through $\phi$: selects an element from $set$, where the probability of each element is proportional to the value of a given function $\phi$\/ defined on $set$.
\end{itemize}

@@

Let $Q  = \{ a^{\pi(k_1)}, a^{\pi(k_2)}, \ldots, a^{\pi(k_{m})} \}$ be the set of consolidated items assembled on the set of $m$ pallets in node $\pi(k)$.

@@

As the number of pallets was small for an integer program solver, the increased time was negligible.

@@

\begin{table}[H]
\centering
\caption{Distance from ramp door minimization}  \label{tab:distRampDoor}
\footnotesize
%\scriptsize
\begin{tabular}{cccc}
\toprule

{\bf Surplus} & {\bf Scenario} & {\bf Before (m)} & {\bf After (m)} \\
\midrule
\multirow{6}{*}{$1.2$}&1 & 7.07 & 7.07 \\
&                     2 & 41.23 & 37.52 \\
&                     3 & 24.03 & 24.64 \\
&                     4 & 26.84 & After \\
&                     5 & Before & After \\
&                     6 & Before & After \\
\midrule
\multirow{6}{*}{$1.5$}&1 & 7.07 & 7.07 \\
&                     2 & 41.23 & 37.52 \\
&                     3 & 24.03 & 24.64 \\
&                     4 & 26.84 & After \\
&                     5 & Before & After \\
&                     6 & Before & After \\
\midrule
\multirow{6}{*}{$2.0$}&1 & 7.07 & 7.07 \\
&                     2 & 41.23 & 37.52 \\
&                     3 & 24.03 & 24.64 \\
&                     4 & 26.84 & After \\
&                     5 & Before & After \\
&                     6 & Before & After \\
\midrule
&                     {\bf Average} & Before & After \\
\bottomrule	
\end{tabular}
%\textsuperscript{asdf sd .}	
\normalsize
\end{table}

>>>>

Given the assumptions, scenarios and parameters described in the previous section, we are ready to present the mathematical modelling of ACLP+RPDP.

@@

Let $S_K = \{s: \{1, \dots, K\} \rightarrow \{1, \dots, K\} \}$ be the set of $K!$ permutations, which correspond to all possible tours (or itineraries) that have $l_0$ as origin and end, passing through the other $K$ nodes.

@@

		{\it Stopping criterion:} & All methods have the same time limit of $1.8$ seconds per node.\\

@@

@@

Let $Q^{\pi(k)}  = \{ a^{\pi(k)}_1, a^{\pi(k)}_2, \ldots, a^{\pi(k)}_m \}$ be the set of consolidated items assembled on the set of $m$ pallets in node $\pi(k)$.

@@

As the number of pallets was small (7 and 18) for an integer program solver, the increased time was negligible (less than 1s).

@@

\begin{table}[H]
\centering
\caption{Distance from ramp door minimization}  \label{tab:distRampDoor}
\footnotesize
%\scriptsize
\begin{tabular}{ccccc}
\toprule

{\it surplus} & {\bf Scenario} & {\bf Before (m)} & {\bf After (m)}  & {\bf Improvement (\%)}  \\
\midrule
\multirow{6}{*}{$1.2$}& 1 & 31.7  & 29.0  & 8.3\\
&                       2 & 195.9 & 195.9 & 0.0\\
&                       3 & 156.0 & 153.6 & 1.5 \\
&                       4 & 143.3 & 143.3 & 0.0 \\
&                       5 & 123.2 & 122.5 & 0.5 \\
&                       6 & 106.5 & 105.7 & 0.8 \\
\midrule
\multirow{6}{*}{$1.5$}& 1 &  31.8 &  28.7 & 9.6 \\
&                       2 & 197.0 & 197.0 & 0.0 \\
&                       3 & 156.3 & 156.3 & 0.0 \\
&                       4 & 143.8 & 143.8 & 0.0\\
&                       5 & 125.0 & 124.2 & 0.7 \\
&                       6 & 108.2 & 107.6 & 0.6\\
\midrule
\multirow{6}{*}{$2.0$}& 1 & 7.07 & 7.07 & \\
&                       2 & 41.23 & 37.52 & \\
&                       3 & 24.03 & 24.64 & \\
&                       4 & 26.84 & After & \\
&                       5 & Before & After & \\
&                       6 & Before & After & \\
\midrule
&                         &        & {\bf Average} & 0.0\\
\bottomrule	
\end{tabular}
%\textsuperscript{asdf sd .}	
\normalsize
\end{table}
